openarchaeoCollaboration

### 2021-06-13 analysis/paper.Rmd
Add total commits to activity vs. lifespan plot

```{r plot-lifespan-vs-rate}
oarch_lifespan %>% 
  ggplot(aes(x = lifespan, y = commit_rate)) +
  geom_point() +
  scale_x_log10() +
  scale_y_log10() +
  labs(
    title = "Project lifespan vs. average commit rate",
    x = "Lifespan (days)", y = "Commits per day",
    caption = "Data: open-archaeo.info and GitHub API"
  )
```

>>>>

```{r plot-lifespan-vs-rate}
oarch_lifespan %>% 
  ggplot(aes(x = lifespan, y = commit_rate, size = n)) +
  geom_point() +
  scale_x_log10() +
  scale_y_log10() +
  labs(
    title = "Project lifespan vs. average commit rate",
    x = "Lifespan (days)", y = "Commits per day", size = "Total commits",
    caption = "Data: open-archaeo.info and GitHub API"
  )
```
